---
title: "Calculate the grading adjustment factor accordinng to WebPA"
---

```{r, include=FALSE, message=FALSE, results='hide', warning=FALSE, error=FALSE}
library(tidyverse)
library(readxl)

options("dplyr.summarise.inform" = FALSE)  # disables warning in dplyr::summary() (experimental lifecycle)
```

```{r}
path_input <- "../input"
path_output <- file.path("../output", "webpa_score.csv")
path_submitted <- file.path(path_input, "submitted_ratings")
```

## List of all students and groups

```{r}
students_group_df <- read_excel(file.path(path_input, "students_groups.xlsx"))
```

## Ratings submitted by students

Read the sizes of the groups from sizes.csv.  
Set path to submissions folder with the following structure:  
```
- submissions/  
  - group_01/  
    - file1.xlsx  (NOTE: the file name doesn't matter)
    - file2.xlsx
    ...
  - group_02/  
    - file1.xlsx
    - file2.xlsx
```

Determine the number of rows to skip based on a sample file
```{r}
sample_xlsx_df <- 
  path_submitted %>% 
  list.files(pattern = '*.xlsx', 
             full.names = TRUE, 
             recursive = TRUE) %>%
  sample(1) %>% 
  read_excel()

nrow_template <- which(sample_xlsx_df[1] == "My name (x)")
```


A function to extract ratings from submitted Excel files:
```{r}
extract_rating <- function(individual_path) {
  a_rating_df <- 
    read_excel(individual_path, skip = nrow_template, 
               col_types = c("text", "text", "numeric", "text", "text")) %>% 
    select(
      `x` = "My name (x)",
      `name` = "Person",
      `rating` = "Rating",
      `comment` = "Comments",
      `group` = "Team")
  
  a_rating_df %>% 
    mutate(rater = a_rating_df$name[which(a_rating_df$x == "x")]) %>% 
    select(ratee = name, rater, group_number = group, rating)
}
```


Extract the ratings into one big tibble.
```{r}
# read submitted Excel file and collect all ratings
rating_input_df <- 
  path_submitted %>% 
  list.files(pattern = '*.xlsx', 
             full.names = TRUE, 
             recursive = TRUE) %>% 
  map_dfr(extract_rating)
```

## WebPA calculation

[WebPA algorithm](http://webpaproject.lboro.ac.uk/academic-guidance/a-worked-example-of-the-scoring-algorithm/)
```{r}
# calculate fudge factor based on the number of received ratings
n_submitted_df <- 
  rating_input_df %>% 
  group_by(group_number) %>% 
  summarize(n_raters = n_distinct(rater))

n_group_df <- 
  students_group_df %>% 
  group_by(Team) %>% 
  summarize(group_size = n()) %>% 
  ungroup() %>% 
  select(group_number = Team, group_size)

fudge_df <-
  n_group_df %>% 
  left_join(n_submitted_df, by = "group_number") %>% 
  mutate(n_raters = replace_na(n_raters, 0)) %>% 
  mutate(fudge_factor = group_size / n_raters) %>% 
  select(group_number, fudge_factor)
      

# perform WebPA calculations
webpa_df <- 
  
  # generate list of all possible raters, cross with ratees
  students_group_df %>%
  select(rater = Person, group_number = Team) %>% 
  mutate(ratee = rater) %>% 
  group_by(group_number) %>% 
  expand(rater, ratee) %>% 
  
  # enter the submitted ratings
  left_join(rating_input_df, 
            by = c("group_number", "rater", "ratee")) %>% 

  # normalize by total given ratings from each rater
  group_by(group_number, rater) %>%
  mutate(rater_total_given = sum(rating, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(norm_received = rating / rater_total_given) %>% 

  # accumulate normalized rating for each ratee
  group_by(group_number, ratee) %>% 
  summarize(sum_norm_received = sum(norm_received, na.rm = TRUE)) %>% 
  ungroup() %>% 
  
  # adjust with the fudge factor
  left_join(fudge_df, by = "group_number") %>% 
  mutate(webpa_score = sum_norm_received * fudge_factor) %>% 

  # handle the case when nobody from the group submitted
  mutate(webpa_score = if_else(is.nan(webpa_score), 1, webpa_score)) %>% 
    
  # keep only relevant columns
  select(group_number, ratee, webpa_score)

```

Save the WebPA score to CSV.
```{r}
webpa_df %>% 
  write_csv(path_output)
```

Check: Adding up all WebPA score for every group should equal to the number of team members in each group
```{r}
webpa_df %>% 
  group_by(group_number) %>% 
  summarize(sum_webpa = sum(webpa_score)) %>% 
  ungroup() %>% 
  left_join(n_group_df, by = "group_number") %>% 
  mutate(is_equal = sum_webpa == group_size)
```

